\begin{abstract}
During the last decade, the blockchain space has exploded with a plethora of new
cryptocurrencies, covering a wide array of different features, performance and
security characteristics.  Nevertheless,  each of these coins functions in a
stand-alone manner, independently.  Sidechains have been envisioned as a
mechanism to allow blockchains to communicate with one   another and, among
other applications,  allow the transfer of value from one chain to another, but
so far  there have been no decentralized constructions.  In this paper, we put
forth the first sidechains construction that allows communication between
proof-of-work blockchains without trusted intermediaries. Our construction is
generic in that it allows the passing of any information between blockchains. It
gives  rise to two illustrative examples: the ``remote ICO,'' in which an
investor pays in currency on one blockchain to receive tokens in another, and
the ``two-way peg,'' in which an asset can be transferred from one chain to
another and back. We pinpoint the features needed for two chains to communicate:
On the source side, a proof-of-work blockchain that has been {\em interlinked},
potentially with a velvet fork; on the destination side, a blockchain with any
consensus mechanism that has sufficient expressibility to implement
verification, such as smart contract support. We put forth the smart contracts
needed to implement these sidechains and explain them in detail. We model our
construction mathematically and give a formal proof of security. In the heart of
our construction, we use a recently introduced cryptographic primitive,
Non-Interactive Proofs of Proof-of-Work (NIPoPoWs). Our security proof uses a
standard computational reduction from our new proof-of-work sidechains protocol
to the security of NIPoPoWs, which has, in turn, been shown to be secure in
previous work. Our working assumption is honest majority in each of the
communicating chains.
\end{abstract}
